Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
earlyoften

Through these changes, our language has the syntax shown in
Figure~\ref{fig:syntax}.  As shown, final states, answers, in the language are
now simple values because there are no exceptions.

@@

\langName has an operational semantics that should be familiar to the reader who
has seen a single step semantics for a basic lambda calculus.  The interesting
additions are the same as those in \origLang, where there are additional rules
for handling the bracketed values.  The reduction rules for the semantics are
given in Figure~\ref{fig:operational_semantics}.

@@

For the sake of being able to discuss how strong labels are in relation to a
type, we follow the example of Simonet and Pottier~\cite{InfoFlowML} and define
a ``guards'' relation between labels and types, denoted $l \guards t$, which
states that the label $l$ is at least as restrictive as the label on the type
$t$.  In other words, this requires that the type has at least $l$ for it's
security label.  The two rules regarding this relationships for both types in
our language are given in Figure~\ref{fig:guard_rules}.

>>>>

Through these changes, our language has the syntax shown in
Figure~\ref{fig:syntax}.  As shown, final states (answers) in the language are
now simple values because there are no exceptions.

@@

\langName has an operational semantics reminiscent of single step semantics for a basic lambda calculus.  The interesting
additions are the same as those in \origLang -- additional rules
for handling the bracketed values.  The reduction rules for the semantics are
given in Figure~\ref{fig:operational_semantics}.

@@

For the sake of being able to discuss how strong labels are in relation to a
type, we follow the example of Simonet and Pottier~\cite{InfoFlowML} and define
a ``guards'' relation between labels and types, denoted $l \guards t$, which
states that the label $l$ is at least as restrictive as the label on the type
$t$.  In other words, this requires that the type has at least $l$ for its
security label.  The two rules regarding this relationships for both types in
our language are given in Figure~\ref{fig:guard_rules}.
